---
title             : "Lab 8 Full Document"
shorttitle        : "Lab 8 Short Title"

author: 
  - name          : "Alexis Adams-Clark"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "2000 Oregon St."
    email         : "aadamscl@uoregon.edu"
  - name          : "Andrew Fridman"
    affiliation   : "1"
  - name          : "Xi Yang"
    affiliation   : "1"
    

affiliation:
  - id            : "1"
    institution   : University of Oregon


authornote:
  I could not remove the author note! ME NEITHER!!!
abstract: |
  Hello, this is the abstract.   Hello, this is the abstract.   Hello, this is the abstract.   Hello, this is the abstract.   Hello, this is the abstract.   Hello, this is the abstract.   Hello, this is the abstract.   Hello, this is the abstract.   Hello, this is the abstract.   Hello, this is the abstract.   Hello, this is the abstract.   Hello, this is the abstract.   Hello, this is the abstract.   Hello, this is the abstract.   Hello, this is the abstract.   Hello, this is the abstract.   Hello, this is the abstract.   Hello, this is the abstract.   Hello, this is the abstract.   Hello, this is the abstract.   Hello, this is the abstract.   Hello, this is the abstract.   Hello, this is the abstract.   Hello, this is the abstract.   Hello, this is the abstract.   Hello, this is the abstract. 
  
  <!-- https://tinyurl.com/ybremelq -->
  
keywords          : "group project, R, github"

bibliography      : ["references.bib"]

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
library(papaja)
library(here)
library(rio)
library(ggplot2)
library(dplyr)
library(knitr)
library(tidyverse)
list.files(here("Data"))
data <- import(here("Data", "star.csv"))
opts_chunk$set(fig.width=6.5, 
               fig.height=8, 
               message = TRUE, 
               warning = FALSE,
               include = TRUE)
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

# Introduction
We cited this paper @rosenbergtidylpa and this paper @oliveira2008balance!

# Methods
We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study. <!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->

## Participants

## Material

## Procedure

## Data analysis

# Results
```{r table, results = 'asis'}
data %>% 
  group_by(sex, frl) %>% 
  summarize(math_mean = mean(tmathss), 
            math_sd = sd(tmathss, na.rm = TRUE), 
            rdg_mean = mean(treadss), 
            rdg_sd = sd(treadss, na.rm = TRUE)) %>% 
  knitr::kable(format = "latex")
```


# Discussion


\newpage

# References
```{r create_r-references}
r_refs(file = "references.bib")
```

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id = "refs"></div>
\endgroup