---
title             : "Lab 8 Full Document"
shorttitle        : "Lab 8 Short Title"

author: 
  - name          : "Alexis Adams-Clark"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "2000 Oregon St."
    email         : "aadamscl@uoregon.edu"
  - name          : "Andrew Fridman"
    affiliation   : "1"
  - name          : "Xi Yang"
    affiliation   : "1"
    

affiliation:
  - id            : "1"
    institution   : University of Oregon


authornote:
  I could not remove the author note! ME NEITHER!!!
abstract: |
  Hello, this is the abstract.   Hello, this is the abstract.   Hello, this is the abstract.   Hello, this is the abstract.   Hello, this is the abstract.   Hello, this is the abstract.   Hello, this is the abstract.   Hello, this is the abstract.   Hello, this is the abstract.   Hello, this is the abstract.   Hello, this is the abstract.   Hello, this is the abstract.   Hello, this is the abstract.   Hello, this is the abstract.   Hello, this is the abstract.   Hello, this is the abstract.   Hello, this is the abstract.   Hello, this is the abstract.   Hello, this is the abstract.   Hello, this is the abstract.   Hello, this is the abstract.   Hello, this is the abstract.   Hello, this is the abstract.   Hello, this is the abstract.   Hello, this is the abstract.   Hello, this is the abstract. 
  
  <!-- https://tinyurl.com/ybremelq -->
  
keywords          : "group project, R, github"

bibliography      : ["references.bib"]

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
library(papaja)
library(here)
library(rio)
library(ggplot2)
library(dplyr)
library(knitr)
library(tidyverse)
list.files(here("Data"))

# Generally, you won't want your data import to go in a "inclue = FALSE" chunk
# The rest of this stuff is good here though.
data <- import(here("Data", "star.csv"))
opts_chunk$set(fig.width=6.5, 
               fig.height=8, 
               message = TRUE, 
               warning = FALSE,
               include = TRUE)
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

# Introduction
We cited this paper @rosenbergtidylpa and this paper @oliveira2008balance!

# Methods
We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study. <!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->

## Participants

## Material

## Procedure

## Data analysis

# Results
Why is this table showing up in text.

```{r table}
data %>% 
  group_by(sex, frl) %>% 
  summarize(math_mean = mean(tmathss), 
            math_sd = sd(tmathss, na.rm = TRUE), 
            rdg_mean = mean(treadss), 
            rdg_sd = sd(treadss, na.rm = TRUE)) %>% 
knitr::kable(format = "latex", 
             booktabs = TRUE,
             caption = "An awesome table")

# Put a caption on it to get it to go where it should. For figs you need to
# include it as a chunk option, which you can see below. Also put 
# `booktabs = TRUE` to make it look nicer. Another alternative is 
# `papaja::apa_table`
```

```{r fig.cap="My amazing figure"}
#Subset data
#View(data)
data_p <- data %>% 
            characterize() %>% 
            select(totexp, tmathss, frl)
#View(data_p) # These bits should be commented out or remved prior to knitting

#Plot data
ggplot(data_p, aes(x=totexp, y=tmathss, color=factor(frl))) +
       geom_point(color="gray") +
       geom_smooth(se=TRUE, method="lm") +
       theme_minimal() +
       theme(legend.position="none") +
       labs(x="Teacher Experience (years)",
            y="Total Math Scale Score",
            title="Relation between teacher experience and math scores",
            subtitle="Separate regression lines displayed by free/reduced prince lunch status")
```


# Discussion


\newpage

# References
```{r create_r-references}
r_refs(file = "references.bib")
```

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id = "refs"></div>
\endgroup